---
title: "Reading data from the web"
author: "Yiying Wu"
date: "2023-10-12"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Extracting tables
### `rvest` and `httr`

```{r}
library(tidyverse)
library(rvest)
library(httr)
```
### import NSDUH data
http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm
```{r}
url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"
drug_use_html = read_html(url)

drug_use_html
```

extracting the tables from the HTML.
```{r}
drug_use_html |>
  html_table()
```

only focused on the first table for now, so get the contents from the first list element.

`first()`: get the first element
```{r}
table_marj = 
  drug_use_html |> 
  html_table() |> 
  first() 

table_marj
```

the “note” at the bottom of the table appears in every column in the first row.  need to remove that using `slice(-1)`
```{r}
table_marj = 
  drug_use_html |> 
  html_table() |> 
  first() |>
  slice(-1) 

table_marj
```

## CSS Selectors
scrape the data about the Star Wars Movies from the IMDB page. The first step is to get the HTML.

https://www.imdb.com/list/ls070150896/
```{r}
swm_html = 
  read_html("https://www.imdb.com/list/ls070150896/")
```

```{r}
swm_html |>
  html_elements(".lister-item-header a")

title_vec = 
  swm_html |>
  html_elements(".lister-item-header a") |>
  html_text()

title_vec

gross_rev_vec = 
  swm_html |>
  html_elements(".text-small:nth-child(7) span:nth-child(5)") |>
  html_text()

runtime_vec = 
  swm_html |>
  html_elements(".runtime") |>
  html_text()

swm_df = 
  tibble(
    title = title_vec,
    rev = gross_rev_vec,
    runtime = runtime_vec)
```

